Optimal Transport Problems

### 2018-04-16 reports/progress-report/progress.tex
notes for ch4

% Page set-up
\usepackage[margin=1.5in]{geometry}
\linespread{1.2}

@@

@@

\section{Theoretical foundations}
The following is a concise review of selected topics in Chapters 2 and 3 in
\cite{peyre2017computational}.

@@

\subsection{Dual-ascent algorithms and Hungarian algorithm}

@@

@@

The Hungarian algorithm's runtime can be visualized, along with a log-log plot
regression,

\begin{figure}[h]
\includegraphics[width=\textwidth]{../../code/hungarianruntime}
\label{fig:hungarianruntime}
\end{figure}

We can also recreate similar plots for the linear-programming algorithm,

\begin{figure}[h]
\includegraphics[width=\textwidth]{../../code/lpruntime}
\end{figure}

@@

The next steps are two-fold. First of all, we will continue our exploration and
analysis of existing algorithms to solve the optimal-transport problem. In
particular, we remain to computationally analyze the dual-ascent algorithms in
generality, and can also explore the auction algorithm. Secondly, we will
attempt to approach the problem from a novel direction, with the ultimate
ambition of arriving at a new algorithm that performs competitively.

>>>>

% Page set-up
\usepackage[margin=1in]{geometry}
\linespread{1.2}

@@

\tableofcontents

@@

\subsection{Theoretical foundations}

The following is a concise review of selected topics in Chapters 2 and 3 in
\cite{peyre2017computational}.

@@

\subsubsection{Dual-ascent algorithms and Hungarian algorithm}

@@

\subsection{Numerical experiments}

@@

The Hungarian algorithm's runtime can be visualized, along with a log-log plot
regression, in \cref{fig:hungarianruntime}. We also include the runtime plots for the simplex algorithm in \cref{fig:hungarianruntime}.

\begin{figure}[h]
\includegraphics[width=\textwidth]{../../code/hungarianruntime}
\includegraphics[width=\textwidth]{../../code/lpruntime}
\caption{Runtime comparison}
\label{fig:hungarianruntime}
\end{figure}

% \begin{figure}[h]
% % \end{figure}
% %

@@

The next steps are two-fold. First of all, we will continue our exploration and
analysis of existing algorithms to solve the optimal-transport problem. In
particular, we remain to computationally analyze the dual-ascent algorithms in
generality, and can also explore the auction algorithm. Secondly, we will
attempt to approach the problem from a novel direction, with the ultimate
ambition of arriving at a new algorithm that performs competitively. There is also a rich literature and ongoing development on approximate optimization methods, e.g. via entropic regularization (Chapter 4 in \cite{peyre2017computational}).
